How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-05-05 tse-paper/content.tex
address todos

With the term ``chunk retrieval technique,'' we refer to a way of
automatically extracting strings that appear literally in build
logs, i.e., techniques that do not aggregate, combine, or deduct
information.
We call such pieces of information in build logs
\emph{chunks}.

@@

\subsubsection{Configuring}
To configure CTS we chose to use the same concept of examples as for
PBE: lines of the targeted chunks from the training examples define
the search query.
Using a Vector Space
Model~\cite{schutze2008introduction} (VSM), an algebraic model for
representing textual documents, we encode each line as a separate term
vector.
The terms that make up the dictionary are simply all words
that appear in the example logs, where we separate words by spaces.
% TODO Caro: complete above sentence if we separate by anything else
The vectors comprise points counting
how many times a word out of the dictionary appears in the specific
line at hand.

@@

\subsection{Keyword Search (KWS)}
When developers scavenge for a specific piece of information within a
large amount of unstructured information, a first ad hoc approach they
use is to search for related keywords.
%% TODO Caro: I took this out as it interrupts reading flow.
%% Do you
%% agree?
%% Indeed, this was one of the
%% most common approaches we took when searching for the reason a build
%% failed while creating the \emph{LogChunks} data
%% set~\cite{brandt2020logchunks}.
% ganz raus

% C: motivation for KWS in LogChunks Paper
% yeah we can maybe leave that out here (move to 'choice for crt'?)

To investigate the performance of this approach, we designed a chunk
retrieval technique mimicking this human behavior based on keyword
search.

\subsubsection{Configuring}
A set of keywords configures the chunk retrieval with KWS\@.
To better
compare KWS with PBE and CTS, we also configure it through examples.
% TODO (resolved) associate is very abstract and tells us
% less about what is going on than the new version

% hope........
% C: explain pure technique vs evaluate-able technique vs comparable
% maybe! we can just replace the hope, or even refer to or logchunks
% experience here / later TODO expect fix sentence!
% TODO CARO extract a list of kewords that expecti nt the spec input and
From each example, we extract a list of keywords that appeared in the
training examples and that we exect to appear
in, or close to, the targeted chunk of new input.
Finally, we merge the lists from all examples to build one unified
list of the most commonly occurring keywords for the search with KWS.

@@

% TODO Caro: I like this explanation of structural categories and
% would leave it here (slightly adapted), but I think
% struct.
%categ.
%should be mentioned earlier -- not sure if you know a
% better place, but how about sec.
%3.1? i don't think people should
% have to read an example section -- which they might skip -- to
% get to know of this important concept!

% C: indeed it's a bit too important to skip
% though can we reasonably explain this without introducing the
% exact techniques first?
% we can also try to start with the example section

When we train PBE with the two examples from \Cref{lst:chunk-example},
it produces a regular expression program similar to the one presented
in
\Cref{lst:prose-program-simplified}.
This shows that the characters structuring the text around the chunk are
crucial for regular expressions to identify a log chunk.
In fact, if we add the third example from
to the training set (which has a
different structural representation),
PBE is not able to synthesize a program anymore and returns
``\texttt{no program found}.''
% adapt because already introduced word TODO Caro
% evtl kann man diesen satz rausnehmen
We later express this difference in structural representation through
separating log chunks into \emph{structural categories}.
The chunks from \Cref{lst:chunk-example}
are in the \emph{same structural category}, while the chunk from
\Cref{lst:chunk-example-3} is in a
\emph{different structural category}.

CTS will rank the lines from an analyzed build log which are most
similar to the chunks in the training examples
from \Cref{lst:chunk-example}.
It will then return the two lines ranked highest, as the chunks in
the training examples have on average 2.0 lines.
% TODO Caro: How well does it deal with the third example?
% TS has so much magic & this example never ran in our study
% note: I include no notice of how 'good' it runs here
% if we look at the used words: they are very different in both examples

@@

The first and most important aspect that influences the decision for a
chunk retrieval technique is the presence of different structural
categories in the log (or lack therefore).
Are the targeted log
chunks always present in the same structural way within the build logs
?  If so, the chunks
in all training examples and the analyzed build log are in the same
structural category (first question in \Cref{fig:crt-recommendation})
% TODO move up pbe then cts and then kws
%TODO ...
%and what? PBE is the best technique?
% C: this is more a clearer 'introduction' to structural categories
% if we believe this to be explained well enough here we can also
% leave it out

% TODO Caro: check that this does not get a mini paragraph
If the chunks are from multiple structural categories and recall is
more important than precision, we recommend to use KWS\@.
% TODO because ?
% C: looking for reference to tree figure or to results section?

If precision is more important than recall, we
recommend CTS, as \Cref{fig:crt-recommendation} shows on the
right half of the decision tree.
We also recommend CTS when the log chunks are
from one structural category, when the user does not require high
confidence in the precision or recall of the outcome, and when one
would rather have output with low recall instead of no output at all.
On the leftmost path of the decision tree,
when the chunks are from one structural category and the user
needs high confidence in the correctness of the output or prefers
no output over output with low recall, we recommend PBE\@.

@@

% TODO Caro: fill in the maven analyzer plugin and others.
% C: aha did we evaluate them?...
% C: so I'll add a few more and anecdotally say what each does?
% the list will be in now way complete but maybe give an impression
% as if we are close to what industry says.
\textbf{Limitation to Scholarly Articles.} We limited our literature
survey to scholarly articles.
However, the field of build log analysis is extremely relevant to
practitioners, too.
While it is difficult to systematically sight all such non-scientific
material, we ran several Google search queries related to build log
analysis and evaluated them informally.
Our findings include the Jenkins build log analyzer and a web page
on which Microsoft details how its CI service, Azure Pipelines, uses a
PBE approach for certain log formats such as Python.
This inspired the choice of PBE in \Cref{sec:choice}.
% TODO Caro: end with claim that we are still close to
% industry approaches

>>>>

With the term ``chunk retrieval technique,'' we refer to a way of
automatically extracting strings that appear literally in build
logs, i.e., techniques that do not aggregate, combine, or deduct
information.
We call such pieces of information in build logs
\emph{chunks}.
Depending on the format of the chunks within the build log we
separate them into different \emph{structural categories}.

@@

\subsubsection{Configuring}
To configure CTS we chose to use the same concept of examples as for
PBE: lines of the targeted chunks from the training examples define
the search query.
Using a Vector Space
Model~\cite{schutze2008introduction} (VSM), an algebraic model for
representing textual documents, we encode each line as a separate term
vector.
The terms that make up the dictionary are simply all words
that appear in the example logs, where we separate words by spaces and
punctuation.
The vectors comprise points counting
how many times a word out of the dictionary appears in the specific
line at hand.

@@

\subsection{Keyword Search (KWS)}
When developers scavenge for a specific piece of information within a
large amount of unstructured information, a first ad hoc approach they
use is to search for related keywords.
To investigate the performance of this approach, we designed a chunk
retrieval technique mimicking this human behavior based on keyword
search.

\subsubsection{Configuring}
A set of keywords configures the chunk retrieval with KWS\@.
To better
compare KWS with PBE and CTS, we also configure it through examples.
From each example, we extract a list of keywords that appeared in the
training examples and that we expect to appear
in, or close to, the targeted chunk in a new build log.
Finally, we merge the lists from all examples to build one unified
list of the most commonly occurring keywords for the search with KWS.

@@

When we train PBE with the two examples from \Cref{lst:chunk-example},
it produces a regular expression program similar to the one presented
in
\Cref{lst:prose-program-simplified}.
This shows that the characters structuring the text around the chunk are
crucial for regular expressions to identify a log chunk.
In fact, if we add the third example from
to the training set (which has a
different structural representation),
PBE is not able to synthesize a program anymore and returns
``\texttt{no program found}.''
The chunks from \Cref{lst:chunk-example}
are in the \emph{same structural category}, while the chunk from
\Cref{lst:chunk-example-3} is in a
\emph{different structural category}.

If we train CTS with the example chunks from
\Cref{lst:chunk-example},
CTS will rank the lines from an analyzed build log which are most
similar to the chunks in the training examples.
It will then return the two lines ranked highest, as the chunks in
the training examples have on average 2.0 lines.
In this example,
CTS will have difficulty extracting the lines from
\Cref{lst:chunk-example-3} as there are no words that appear
in both the training and the test chunks.
The same applies if we train with the first chunk from
\Cref{lst:chunk-example} and try to retrieve the second chunk,
as the only shared word is ``task''.

@@

The first and most important aspect that influences the decision for a
chunk retrieval technique is the presence of different structural
categories in the log (or lack therefore).
Are the targeted log
chunks always present in the same structural way
within the build logs? If so, the chunks
in all training examples and the analyzed build log are in the same
structural category (first question in \Cref{fig:crt-recommendation}).

On the leftmost path of the decision tree,
when the chunks are from one structural category and the user
needs high confidence in the correctness of the output or prefers
no output over output with low recall, we recommend PBE\@.
If the user does not
require high confidence in the correctness of the output and prefers
to receive some output even with low recall, we recommend CTS\@.

On the rightmost path of the decision tree,
if the chunks are from multiple structural categories and recall is
more important than precision, we recommend to use KWS\@.
If precision is more important than recall, we
recommend CTS\@.

@@

% M: fill in the maven analyzer plugin and others.
% C: added to the jenkins bl analyzer, though I left out th maven
% analyzer cause it has 1 star on github so kinda not 'industry' grade
\textbf{Limitation to Scholarly Articles.} We limited our literature
survey to scholarly articles.
However, the field of build log analysis is extremely relevant to
practitioners, too.
While it is difficult to systematically sight all such non-scientific
material, we ran several Google search queries related to build log
analysis and evaluated them informally.
Our findings include the Jenkins build log
analyzer~\cite{jenkins2020failure-analyzer}, where a user can
define custom regular expressions to parse a build log, and a web page
on which Microsoft details how its CI service, Azure Pipelines, uses a
PBE approach for certain log formats such as Python.
This inspired the choice of PBE in \Cref{sec:choice}.
Our impression is that non-scientific tools are often based on
parsing with the help of regular expressions---similar to the
techniques mentioned in scientific literature and the PBE technique
we proposed.
